Title

### 2024-01-02 Quarto Template.qmd
Update Quarto Template.qmd

```{r setup}
#| include: false
library(tidyverse)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows"="C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```
